The hydra and the rooster

### 2020-07-07 latex/chapter-skippable.tex
restructuration of Gamma0

Finally, it is interesting to show that the segment $[0,n[$ is a ``sub-segment'' of
$[0,n+1[$. Since types $t\;n$ are $t\;(n+1)$ are not convertible, we consider a ``cast'' 
function $\iota$ from $t\;n$ to $t\;(n+1)$, and prove this function is  a bijection  from $t\;n$ to
the segment $[0,n-1[$ of $t\;(n+1)$.

@@

Coming back to finite ordinals, the conversion function from $t\;i$ to $t\;j$ is
defined with \texttt{Program}.

\begin{Coqsrc}
Program Definition iota {i j : nat}  (H: i < j) (alpha: t i) : t j :=
  alpha.

Lemma iota_compare_commute (i j  :nat)(H : i < j) :
  forall alpha beta, compare alpha beta = compare (iota  H alpha)
                                                  (iota  H beta).
\end{Coqsrc}

We are now able to build an instance of \texttt{Subsegment}

@@

   Program Definition iota  (alpha: t i) : t j :=  alpha.

@@

  Instance F_incl_ij  : SubSegment  (FinOrd i) (FinOrd j) b iota.

>>>>

Finally, it is interesting to show that, if $i<j$, then the segment $[0,i[$ is a ``sub-segment'' of
$[0,j[$. Since the terms  $t\;i$ and $t\;j$ are not convertible, we consider a ``cast'' 
function $\iota$ from $t\;i$ to $t\;j$, and prove this function is  a bijection  from $t\;i$ to
the segment $[0,i[$ of $t\;j$.

@@

\index{Coq!Commands!Program}

We are now able to build an instance of \texttt{Subsegment}.

@@

   Remark Ltb_ij : Nat.ltb i j.
   Program Definition iota_ij  (alpha: t i) : t j :=  alpha.

@@

   Global Instance F_incl_ij  : SubSegment  (FinOrd i) (FinOrd j) b iota_ij.
  (* ... *)
